Thermodynamic fragments for magic states in quantum computation

### 2021-03-28 magic_paper.tex

Within the Wigner representation all negatively represented states are magic states, although in general the converse is not true. However, it is known that all positively represented states used in Clifford circuits admit an efficient classical description, and therefore it is natural to consider focus on describing those negatively represented magic states. The free states in any magic theory must therefore lie in the set
\begin{equation}
    \Fmax \coloneqq \{ \rho: \W[\bmx]{\rho} \geq 0 \text{ for all } \bmx \in \cal{P}_d\}.
\end{equation}
Our focus is on states with negativity, and so the particular choice of free states is not so important for our analysis. The remaining component that needs addressing is the set of quantum operations that is considered free, or easy. Stabilizer operations are the most natural set of operations as they admit a classically efficient description for uniform quantum circuits. However, other choices of operations have been considered in the literature \ddd{[CITE]}. Common to these theories is that free $\E$  is such that $id \otimes \E (\rho)$ has a positive Wigner distribution whenever $ \rho$ has a positive Wigner distribution. Therefore the condition that $\E$ does not generate Wigner negativity is an essential requirement of any magic theory.

>>>>

Within the Wigner representation all negatively represented states are magic states, although in general the converse is not true. However, it is known that all positively represented states used in Clifford circuits admit an efficient classical description, and therefore it is natural to consider focus on describing those negatively represented magic states. The free states in any magic theory must therefore lie in the set
\begin{equation}
    \Fmax \coloneqq \{ \rho: \W[\bmx]{\rho} \geq 0 \text{ for all } \bmx \in \cal{P}_d\}.
\end{equation}
Our focus is on states with negativity, and so the particular choice of free states is not so important for our analysis. The remaining component that needs addressing is the set of quantum operations that is considered free, or easy. Stabilizer operations are the most natural set of operations as they admit a classically efficient description for uniform quantum circuits. However, other choices of operations have been considered in the literature~\cite{cit:ahmadi, cit:seddon, Wang_2019}. Common to these theories is that free $\E$  is such that $(\id \otimes \E) (\rho)$ has a positive Wigner distribution whenever $ \rho$ has a positive Wigner distribution. \nick{This is not true for stabilizer-preserving operations~\cite{cit:ahmadi}, since ``completely'' stabilizer-preserving operations~\cite{cit:seddon} is a strict subset} Therefore, the condition that $\E$ does not generate Wigner negativity is an essential requirement of any magic theory.
